D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-21 ootavacuous.tex
Remove backwards references from Section 8.3
("Semantic Dependencies and Tooling")

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Where a C++ implementation's primary function is to correctly execute
a C++ program, the function of tooling is often to evaluate properties
of possible executions of that same program.
This difference in function results in different sensitivities to
sdep misclassifications, as shown in
Table~\ref{tab:Semantic-Dependency Classification For Tools}.

@@

However, there is an important special case for tools that are closely
associated with a C++ implementation.
Such tools can simply use that implementation's classification of
dependencies as semantic on the one hand or nonsemantic on the
other, whether by working with that implementation's intermediate
representations, binaries produced by that implementation, by tracing
the program's execution, or, in the case of dynamic tools, by actually
executing the program.
While taking this approach sacrifices significant generality, it has the
significant benefit of greatly reducing the cost of dependency analysis,
potentially all the way down to zero.

>>>>

Where a C++ implementation's primary function is to correctly execute
a C++ program, the function of tooling is often to evaluate properties
of possible executions of that same program.
While implementations are never supposed to break a semantic dependency,
tools are in some cases permitted to misclassify them, as shown in
Table~\ref{tab:Semantic-Dependency Classification For Tools}.

@@

However, there is an important special case for tools that are closely
associated with a C++ implementation.
Such tools can simply use that implementation's classification of
dependencies as semantic on the one hand or nonsemantic on the
other, whether by working with that implementation's intermediate
representations, binaries produced by that implementation, by tracing
the program's execution, or, in the case of dynamic tools, by actually
executing the program.
Either way, this approach reduces the problem of analysis from the
level of the C++ abstract machine to a much simpler lower level of
abstraction.
While taking this approach sacrifices significant generality, it also
has the significant benefit of greatly reducing the cost of dependency
analysis, potentially all the way down to zero.
